Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits

### 2018-11-07 Manuscript_draft/Manuscript_draft.Rmd
some editing

---
title: 'How phylogenetic relatedness and floral traits are involved in heterospecifc pollen effect in an artificial co-flowering community'

author:

- name: Jose B. Lanuza
  affilnum: '1,2'

- name:  
  affilnum: 3
  email: barragansljose@gmail.com

affiliation:

- affilnum: 1
  affil: US Environmental Protection Agency, Office of Research and Development, National Health and Environmental Effects Research Laboratory, Atlantic Ecology Division, 27 Tarzwell Drive  Narragansett, RI, 02882, USA

- affilnum: 2
  affil: Big Name University, Department of R, City, BN, 01020, USA

- affilnum: 3
  affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain

output:

  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
    includes:
      in_header: header.tex

  html_document: null

  word_document: null

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
footerdate: yes
abstract: no
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

---

@@

# INTRODUCTION

>>>>

---
title: Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits 
author:
- affilnum: '1,2'
  name: Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
- affilnum: 3
  email: barragansljose@gmail.com
  name: null
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
- affil: Big Name University, Department of R, City, BN, 01020, USA
  affilnum: 2
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 3
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  word_document: null
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---

@@

# INTRODUCTION
[Cut and paste some paragraphs from your literature review/ proposal](Romina)

### 2018-11-07 Manuscript_draft/Manuscript_draft.tex
some editing

\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={How phylogenetic relatedness and floral traits are involved in heterospecifc pollen effect in an artificial co-flowering community},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\title{How phylogenetic relatedness and floral traits are involved in
heterospecifc pollen effect in an artificial co-flowering community}
\author{
Jose B. Lanuza
true
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge How phylogenetic relatedness and floral traits are involved in
heterospecifc pollen effect in an artificial co-flowering community
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza \textsuperscript{1,2} 
true
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
\\*
\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
\\*
\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\title{Working title, The impact of heterospecific pollen on plant reproductive
success is mediated by phylogenetic distance and floral reproductive
traits}
\author{
Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
true
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Working title, The impact of heterospecific pollen on plant reproductive
success is mediated by phylogenetic distance and floral reproductive
traits
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader \textsuperscript{1,2} 
true
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
\\*
\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
\\*
\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

\href{Romina}{Cut and paste some paragraphs from your literature review/
proposal}
